Some examples in extended logic counting classes

### 2017-01-06 LICS/beyond.tex
arregle un label
sin comentarios

It was shown in \cite{I86,I88} that first-order logic extended with a transitive closure operator captures $\nlog$. Inspired by this work, we extend the definition of $\qfo$ with an operator for counting the number of paths in a directed graph, and we show that it can be used to capture $\shl$. Besides, we show that the same idea can be used to extend $\qso$ allowing to capture harder complexity classes.

>>>>

It was shown in \cite{I86,I88} that $\fo$ extended with a transitive closure operator captures $\nlog$. Moreover, it was shown in \cite{I83} that $\so$ extended with a transitive closure operator captures $\pspace$. Inspired by this work, we extend the definition of $\qfo$ with an operator for counting the number of paths in a directed graph, and we show that it can be used to capture $\shl$. Besides, we show that the same idea can be used to extend $\qso$ allowing to capture harder complexity classes.
